Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-30 preliminaries.tex
Add revision action items

@@

@@

@@

\begin{definition}
	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
	We say it is a prototol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
\begin{itemize}
		\item On public inputs $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
		\item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
		$\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
		\item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
	\end{itemize}
\end{definition}

@@

@@

@@

\subsection{Chernoff bound}

@@

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
\begin{definition}
	A quantum leveled homomophic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
	$\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
	\begin{itemize}
		\item \emph{Key generation.}
			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda, 1^L)$ takes a unary representation of the security parameter and a unary representation of the level parameter as inputs and outputs a public key $pk$ and a secret key $sk$.
		\item \emph{Encryption.}
			The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ as inputs and outputs a ciphertext $c$.
		\item \emph{Decryption.}
			The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ as inputs and outputs a message $\mu^*\in\zo$.
			It must be the case that
				$$\QDec(sk, \QEnc(pk, \mu))=\mu$$
			with overwhelming probability in $\lambda$.
		\item \emph{Homomorphic Evaluation.}
			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit $f$ of depth at most $L$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ as inputs and outputs a ciphertext $c_f$.
			It must be the case that
				$$\QDec(sk, \QEval(pk, f, c_1, \ldots, c_l))=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))$$
			with overwhelming probability in $\lambda$.
	\end{itemize}
\end{definition}

>>>>

\Ethan{After this point, add more remarks in this section}

@@

\Ethan{see Scott's paper to see why inverse poly there. Maybe it's just because it's required for his result to work.
More generally, need discussions on sampling vs non sampling
Try to claim our definitions is WLOG/general/intuitive
}

@@

\Ethan{``Streaming" model; can send qubits one-by-one to let client measure many qubits this way.

Tone: Review/introduce. It's not new. Use Urmila's use case as example.}

@@

\Ethan{Need discussion for dfn. 2.7.
Currently there's a remark after about not needing soundness error.
Discuss more.

Difference between SampBQP and BQP definitions.
In particular, SampBQP has additional output (not 0/1).

Two sources of error. Kinda like ``DI" device independent/QKD?
Condition on acc...
Really depends on target audience. If not crypto...

Maybe just remark that there are 2 params but this definition captures both

Again, it's different from BQP so explain why/where.
Make it more friendly to people who aren't familiar with this approach.

Also discuss whether soundness error needs additional param. besides inherited from SampBQP}

\begin{definition}
    Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
    We say it is a protocol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
\begin{itemize}
        \item On public inputs $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
        \item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
        $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
        \item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
    \end{itemize}
\end{definition}

@@

\Ethan{The following is more crypto based

Others don't have a fully general definition,
or it's just statistical/OTP.

Need explanation/discussion for this.
Nobody else writes it like this,
but this is the correct way to write it.

Explain what is this saying.}

@@

\Ethan{Maybe swap 2.9 and 2.8 or move it up even more.
If it's before 2.7 then we can just write 2.7 in terms of this.

Consider making this its own section.}

@@

\Ethan{Chernoff bound looks like it's in the middle of nowhere. Just get rid of it.}

\iffalse
\subsection{Chernoff bound}

@@

\Ethan{This section should be fine; just leave it alone.
It's just technicalities copied from another paper.}

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
\begin{definition}
    A quantum leveled homomorphic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
    $\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
    \begin{itemize}
        \item \emph{Key generation.}
            The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda, 1^L)$ takes a unary representation of the security parameter and a unary representation of the level parameter as inputs and outputs a public key $pk$ and a secret key $sk$.
        \item \emph{Encryption.}
            The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ as inputs and outputs a ciphertext $c$.
        \item \emph{Decryption.}
            The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ as inputs and outputs a message $\mu^*\in\zo$.
            It must be the case that
                $$\QDec(sk, \QEnc(pk, \mu))=\mu$$
            with overwhelming probability in $\lambda$.
        \item \emph{Homomorphic Evaluation.}
            The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit $f$ of depth at most $L$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ as inputs and outputs a ciphertext $c_f$.
            It must be the case that
                $$\QDec(sk, \QEval(pk, f, c_1, \ldots, c_l))=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))$$
            with overwhelming probability in $\lambda$.
    \end{itemize}
\end{definition}

### 2020-04-30 qpip0.tex
Add revision action items

In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gives a $\QPIP_0$ protocol for $\BQP$ languages.
The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
Intuitively, the verifier chooses a string $h$ specifying  the measurement he wants to make, and sends encoded $h$ to the prover. The prover ``commits" to a state $\rho$ with the encoded $h$ and replies. The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}. He sends his choice between the two to the prover and has the  prover reply. If the verifier chose testing, he checks the prover's two replies and rejects if he sees an inconsistency. If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho,h)$ based on the replies. Mahadev~\cite{FOCS:Mahadev18a} proves a ``binding" property of the above protocol: if a prover's strategy would always succeeds on the testing round, then that strategy must binds to a $\rho$, meaning that no matter what $h$ the verifier has picked at the beginning, the verifier can get $M_{XZ}(\rho,h)$  with the same $\rho$ if he had chosen the Hadamard round.

@@

    Protocol:
    \begin{enumerate}
        \item \label{step:naive1} The verifier chooses a $XZ$-measurement $h$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
        \item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
        \item \label{step:urmila-in-naive}
            The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
            \begin{enumerate}
                \item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover.
                \item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$ and sends $y$ to the verifier.
                    Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
                \item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\cVNaive{3}()$  and sends it to the prover.
                \item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
                \item
                    If it is a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
                    If it is a Hadamard round, the verifier obtains $v$.
            \end{enumerate}
        \item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$
    \end{enumerate}
\end{protocol}

@@

Now we are ready to prove Theorem~\ref{thm:qpip0}
\begin{proof}

>>>>

In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gives a $\QPIP_0$ protocol for $\BQP$ languages.
The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
Intuitively, the verifier chooses a string $h$ specifying  the measurement he wants to make, and sends encoded $h$ \Ethan{what?} to the prover. The prover ``commits" to a state $\rho$ with the encoded $h$ and replies. The verifier then uniformly chooses between two options: do a \emph{testing round} or do a \emph{Hadamard round}. He sends his choice between the two to the prover and has the  prover reply. If the verifier chose testing, he checks the prover's two replies and rejects if he sees an inconsistency. If the verifier chose the Hadamard round, he calculates $M_{XZ}(\rho,h)$ based on the replies. Mahadev~\cite{FOCS:Mahadev18a} proves a ``binding" property of the above protocol: if a prover's strategy would always succeeds on the testing round, then that strategy must binds to a $\rho$, meaning that no matter what $h$ the verifier has picked at the beginning, the verifier can get $M_{XZ}(\rho,h)$  with the same $\rho$ if he had chosen the Hadamard round.

@@

    Protocol:
    \begin{enumerate}
        \item \label{step:naive1} The verifier chooses a $XZ$-measurement $h$ from the distribution specified in \stepref{qpip1-verify} of $\PiSamp$.
        \item \label{step:naive2} The prover prepares $\rho$ by running \stepref{qpip1-state-gen} of $\PiSamp$.
        \item \label{step:urmila-in-naive}
            The verifier and prover run $(\PMeasure(\rho), \VMeasure(h))(1^\lambda)$.
            \begin{enumerate}
                \item The verifier samples $(pk, sk)\leftarrow\cVNaive{1}(1^\lambda, h)$ and sends $pk$ to the prover.
                \item The prover runs $(y, \sigma)\leftarrow\cPNaive{2}(pk, \rho)$ and sends $y$ to the verifier.
                    Here we allow the prover to abort by sending $y=\bot$, which does not benefit cheating provers but is useful for analysis.
                \item\label{step:c-urmila-in-naive} The verifier samples $c\leftarrow\cVNaive{3}()$ \Ethan{Just give it sec. param even though it's just a public coin. Just so it doesn't look strange.} and sends it to the prover.
                \item The prover replies $a\leftarrow\cPNaive{4}(pk, c, \sigma)$.
                \item
                    If it is a testing round, the verifier accepts or rejects based on the outcome of $\PiMeasure$.
                    If it is a Hadamard round, the verifier obtains $v$.
            \end{enumerate}
        \item \label{step:naive-output} If it's a Hadamard round, the verifier finishes the verification step of Protocol~\ref{ProtoQPIP1} by generating and outputting $(d, z)$
    \end{enumerate}
\end{protocol}

@@

Now we are ready to prove Theorem~\ref{thm:qpip0}

\Ethan{Try to cut the proof into two: point-wise and average arguments. Figure out what does z-good mean intuitively.

Also more comments/remarks/discussions. Subnormalized state and stuff.}

\begin{proof}
